Train BrainAGE with tidymodels

### 2023-11-16 PaperAnalyses&Figures.Rmd
Cleaned up original script, and added code for descriptive statistics. For revision script, updated code for variable importance, edited figures to save in tiff format and arrange in proper formatting for manuscript. In model training script, updated model names for clarity after incorporation of ComBat pipeline.

packages <-  c("tidyverse",
               "ggpubr", 
               "apaTables", "MetBrewer",
               "ggseg", "vip", "tidymodels")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```
Load Data
```{r}
# BrainAGE and Behavioral Data - Vlad's Model, Baseline
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/BrainagePDSBaseline.Rda")

@@

**Vlad's Model, Baseline Analyses**
Run Models
```{r}
# brainage ~ youth sum
#baseline_puberty_y_sum_1 <- lm(corrected_gap ~ youth_sum, data = sample_1)
#baseline_puberty_y_sum_2 <- lm(corrected_gap ~ youth_sum, data = sample_2)

@@

summary(baseline_cognition_zscore_1_m)
summary(baseline_cognition_zscore_2_m)

@@

@@

Demographics for Baseline Sample
```{r}
table(brainage_pds_baseline$sex)

#white
table(demographics_baseline$demo_race_a_p___10)

@@

#hispanic or latino
table(demographics_baseline$demo_ethn_v2)

@@

@@

demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 == 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

@@

## Model Summaries
```{r}
summary(followup_puberty_y_mean_1)
summary(followup_puberty_y_mean_2)

summary(followup_puberty_p_mean_1)
summary(followup_puberty_p_mean_2)

@@

@@

summary(abcd_baseline_cognition)

summary(abcd_baseline_cognition_standard)
```
Model Plots
```{r}
#Cognition
ggPredict(abcd_baseline_cognition_standard,se=TRUE)

>>>>

packages <-  c("tidyverse",
               "ggpubr", 
               "apaTables", "MetBrewer",
               "ggseg", "vip", "tidymodels", "psych")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}
lapply(packages, library, character.only = TRUE)
```
Load Data
```{r}
# BrainAGE and Behavioral Data - Vlad's Model, Baseline
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/BrainagePDSBaseline.Rda")

@@

**Vlad's Model, Baseline Analyses**

Run Models
```{r}
# brainage ~ youth sum
#baseline_puberty_y_sum_1 <- lm(corrected_gap ~ youth_sum, data = sample_1)
#baseline_puberty_y_sum_2 <- lm(corrected_gap ~ youth_sum, data = sample_2)

@@

summary(baseline_cognition_standard_1)
summary(baseline_cognition_standard_2)

summary(baseline_cognition_zscore_1)
summary(baseline_cognition_zscore_2)

@@

Descriptive Stats
```{r}
describe(sample_1_baseline_months)

describe(sample_2_baseline_months)

nrow(sample_1_baseline_months %>% filter(sex == "F"))

nrow(sample_2_baseline_months %>% filter(sex == "F"))

@@

Demographics for Baseline Sample
```{r}
#white
table(demographics_baseline$demo_race_a_p___10)

@@

#hispanic or latino
table(demographics_baseline$demo_ethn_v2)
```

```{r}
#sex
table(brainage_pds_baseline$sex)

@@

demographics_baseline %>% 
  filter(((demo_race_a_p___10 == 1 | demo_race_a_p___11 == 1) & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & demo_race_a_p___14 != 1 & demo_race_a_p___15 != 1 & demo_race_a_p___16 != 1 & demo_race_a_p___17 != 1 & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1 & demo_race_a_p___25 != 1) & demo_ethn_v2 == 1)

@@

demographics_baseline %>% 
  filter(demo_race_a_p___10 != 1 & demo_race_a_p___11 != 1 & demo_race_a_p___12 != 1 & demo_race_a_p___13 != 1 & (demo_race_a_p___14 == 1 | demo_race_a_p___15 == 1 | demo_race_a_p___16 == 1 | demo_race_a_p___17 == 1 | demo_race_a_p___25 == 1) & demo_race_a_p___18 != 1 & demo_race_a_p___19 != 1 & demo_race_a_p___20 != 1 & demo_race_a_p___21 != 1 & demo_race_a_p___22 != 1 & demo_race_a_p___23 != 1 & demo_race_a_p___24 != 1)

@@

## Model Summaries
```{r}
# Youth-report puberty
summary(followup_puberty_y_mean_1)
summary(followup_puberty_y_mean_2)

# Parent-report puberty
summary(followup_puberty_p_mean_1)
summary(followup_puberty_p_mean_2)

@@

Descriptive Stats
```{r}
describe(sample_1_followup_months)

describe(sample_2_followup_months)
```

@@

#summary(abcd_baseline_cognition)

summary(abcd_baseline_cognition_standard)
```

Descriptive Stats
```{r}
describe(abcd_baseline_months)
```

Model Plots
```{r}
#Cognition
ggPredict(abcd_baseline_cognition_standard,se=TRUE)

### 2023-11-16 Revisions_Analyses&Figures.Rmd
Cleaned up original script, and added code for descriptive statistics. For revision script, updated code for variable importance, edited figures to save in tiff format and arrange in proper formatting for manuscript. In model training script, updated model names for clarity after incorporation of ComBat pipeline.

Install combat
```{r}
library(devtools)
install_github("jfortin1/neuroCombatData")
install_github("jfortin1/neuroCombat_Rpackage")

@@

vip(fit_workflow_combat, num_features=20) +
  theme_light()
ggsave(filename="model2_vip_baseline.png",
                          width=7, height=4, units='in', dpi=300)

@@

vip(fit_workflow_combat_followup, num_features=20) +
  theme_light()
ggsave(filename="model2_vip_followup.png",
                          width=7, height=4, units='in', dpi=300)
## from model code

@@

abcd_vi_dk <- left_join(vi(abcd_model_obj_combat), abcd_vi_renamed_dk)

@@

ggplot(dk_vi_vol) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal_combat.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal_combat.png",
                          width=7, height=4, units='in', dpi=300)

#troubleshooting names
aseg_labs <- brain_labels(aseg) |> 
  as.character()
aseg_vi$label[!aseg_vi$label %in% aseg_labs]
aseg_labs[!aseg_labs %in% aseg_vi$label]

@@

@@

@@

#Youth-Report Puberty
youth_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))),  #,'#526D37'
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12)) 
ggsave(filename="baseline_youth_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

@@

```
```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_followup_combat <-  brainage_pds_followup_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")))

@@

ggarrange(youth_pds_followup_mod1_plot, parent_pds_followup_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
ggsave(filename = "distributions_followup_mod1_combat.png",
                          width=10, height=4, units='in', dpi=300)

@@

@@

@@

vip(fit_workflow_combat_followup, num_features = 20)

@@

ggplot(dk_vi_vol_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(dk_vi_area_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_coronal_followup.png",
                          width=7, height=4, units='in', dpi=300)

ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal_followup.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggplot(data = brainage_both_waves_long %>% filter(src_subject_id %in% brainage_slope_count$src_subject_id) %>% 
                              group_by(src_subject_id) %>%
                mutate(slope = diff(corrected_gap)),
       aes(x = truth, y = corrected_gap, group = src_subject_id, color = slope > 0)) +
    geom_line(size = .2, alpha=0.4) +
  labs(x= "Chronological Age", y = "Corrected Gap") +
  scale_color_manual(name = "Direction of Change", labels = c("Negative", "Positive"), values = c("#E76F51",'#CCDDBB')) +
  theme_minimal()

@@

ggplot(data = brainage_abcd_both_waves_long %>% filter(src_subject_id %in% brainage_abcd_slope_count$src_subject_id) %>% 
                              group_by(src_subject_id) %>%
                mutate(slope = diff(corrected_gap)),
       aes(x = truth, y = corrected_gap, group = src_subject_id, color = slope > 0)) +
    geom_line(size = .2, alpha=0.4) +
  labs(x= "Chronological Age", y = "Corrected Gap") +
  scale_color_manual(name = "Direction of Change", labels = c("Negative", "Positive"), values = c("#E76F51",'#CCDDBB')) +
  theme_minimal()

@@

>>>>

Load Packages
```{r}
#library(devtools)
#install_github("jfortin1/neuroCombatData")
#install_github("jfortin1/neuroCombat_Rpackage")

@@

vip_abcd_baseline <- vip(fit_workflow_combat, num_features=20) +
  theme_light()

ggsave(filename="model2_vip_baseline.png",
                          width=7, height=4, units='in', dpi=300)

@@

vip_abcd_followup <- vip(fit_workflow_combat_followup, num_features=20) +
  theme_light()
ggsave(filename="model2_vip_followup.png",
                          width=7, height=4, units='in', dpi=300)
## from model code

@@

#abcd_vi_dk <- left_join(vi(abcd_model_obj_combat), abcd_vi_renamed_dk)

abcd_vi_dk <- left_join(vi_updated, abcd_vi_renamed_dk)

@@

abcd_model_dk_vol_importance_baseline <- ggplot(dk_vi_vol) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")

ggsave(filename="abcd_model_dk_vol_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

@@

abcd_model_dk_area_importance_baseline <- ggplot(dk_vi_area) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")

ggsave(filename="abcd_model_dk_area_importance_combat.png",
                         width=8, height=4, units='in', dpi=300)

@@

abcd_model_aseg_importance_coronal_baseline <- ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')  +
  labs(title = "Subcortical Volume")
ggsave(filename="abcd_model_aseg_importance_coronal_combat.png",
                          width=7, height=4, units='in', dpi=300)

abcd_model_aseg_importance_sagittal_baseline <- ggplot(aseg_vi) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') 
ggsave(filename="abcd_model_aseg_importance_sagittal_combat.png",
                          width=7, height=4, units='in', dpi=300)

# make one aseg figure
abcd_model_aseg_importance_baseline <- ggarrange(abcd_model_aseg_importance_coronal_baseline, abcd_model_aseg_importance_sagittal_baseline, 
          ncol = 1, nrow = 2)

# Save as final figure
ggarrange(vip_abcd_baseline, abcd_model_dk_vol_importance_baseline, abcd_model_dk_area_importance_baseline, abcd_model_aseg_importance_baseline, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
ggsave(filename = "mod2_vip_ggseg.tiff",
                          width=12, height=12, units='in', dpi=300)

```{r}
#troubleshooting names
aseg_labs <- brain_labels(aseg) |> 
  as.character()
aseg_vi$label[!aseg_vi$label %in% aseg_labs]
aseg_labs[!aseg_labs %in% aseg_vi$label]

@@

ggsave(filename = "pred_bias_mod1_combat.tiff",
                          width=10, height=10, units='in', dpi=300)

@@

ggsave(filename = "pred_bias_mod2_combat.tiff",
                          width=10, height=10, units='in', dpi=300)

@@

#Youth-Report Puberty
youth_pds_baseline_mod1_plot <- ggpar((categorical_pds_baseline_combat %>% 
  filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", color= "youth_pds_cat", fill= "youth_pds_cat", add="mean", palette = c('#3E502A','#7CA352','#A1C181', '#CCDDBB'))),  #,'#526D37'
  xlab="Brain Age Gap", ylab="Density", legend.title = "Youth-Report PDS", font.legend = 8) +
  theme(text = element_text(size = 12))

ggsave(filename="baseline_youth_pds_mod1_combat.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggsave(filename = "distributions_baseline_mod1_combat.tiff",
                          width=7, height=5, units='in', dpi=300)

```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
categorical_pds_followup_combat <-  brainage_pds_followup_combat %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")))

@@

ggarrange(youth_pds_followup_mod1_plot, parent_pds_followup_mod1_plot, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave(filename = "distributions_followup_mod1_combat.png",
                          width=10, height=4, units='in', dpi=300)

ggsave(filename = "distributions_followup_mod1_combat.tiff",
                          width=10, height=4, units='in', dpi=300)

@@

ggsave(filename = "distributions_baseline_mod2_combat.tiff",
                          width=7, height=5, units='in', dpi=300)

@@

ggsave(filename = "distributions_followup_mod2_combat.tiff",
                          width=10, height=4, units='in', dpi=300)

@@

vip_abcd_followup <- vip(fit_workflow_combat_followup, num_features = 20)

@@

abcd_model_dk_vol_importance_followup <- ggplot(dk_vi_vol_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Volume")
ggsave(filename="abcd_model_dk_vol_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

abcd_model_dk_area_importance_followup <-ggplot(dk_vi_area_followup) +
  geom_brain(atlas = dk, position = position_brain(hemi ~ side), aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Cortical Area")
ggsave(filename="abcd_model_dk_area_importance_followup.png",
                         width=8, height=4, units='in', dpi=300)

@@

abcd_model_aseg_importance_coronal_followup <- ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="coronal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51') +
  labs(title = "Subcortical Volume")
ggsave(filename="abcd_model_aseg_importance_coronal_followup.png",
                          width=7, height=4, units='in', dpi=300)

abcd_model_aseg_importance_sagittal_followup <- ggplot(aseg_vi_followup) +
  geom_brain(atlas = aseg, side="sagittal", aes(fill = Importance))+
  theme_void() +
  scale_fill_gradient(low = '#FDD872', high = '#E76F51')
ggsave(filename="abcd_model_aseg_importance_sagittal_followup.png",
                          width=7, height=4, units='in', dpi=300)

# make one aseg figure
abcd_model_aseg_importance_followup <- ggarrange(abcd_model_aseg_importance_coronal_followup, abcd_model_aseg_importance_sagittal_followup, 
          ncol = 1, nrow = 2)

# Save as final figure
ggarrange(vip_abcd_followup, abcd_model_dk_vol_importance_followup, abcd_model_dk_area_importance_followup, abcd_model_aseg_importance_followup, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
ggsave(filename = "mod2_vip_ggseg_followup.tiff",
                          width=12, height=12, units='in', dpi=300)

@@

mod1_longitudinal <- ggplot(data = brainage_both_waves_long %>% filter(src_subject_id %in% brainage_slope_count$src_subject_id) %>% 
                              group_by(src_subject_id) %>%
                mutate(slope = diff(corrected_gap)),
       aes(x = truth, y = corrected_gap, group = src_subject_id, color = slope > 0)) +
    geom_line(size = .2, alpha=0.4) +
  labs(x= "Chronological Age", y = "Corrected Gap") +
  scale_color_manual(name = "Direction of Change", labels = c("Negative", "Positive"), values = c("#E76F51",'#CCDDBB')) +
  theme_minimal()

@@

mod2_longitudinal <- ggplot(data = brainage_abcd_both_waves_long %>% filter(src_subject_id %in% brainage_abcd_slope_count$src_subject_id) %>% 
                              group_by(src_subject_id) %>%
                mutate(slope = diff(corrected_gap)),
       aes(x = truth, y = corrected_gap, group = src_subject_id, color = slope > 0)) +
    geom_line(size = .2, alpha=0.4) +
  labs(x= "Chronological Age", y = "Corrected Gap") +
  scale_color_manual(name = "Direction of Change", labels = c("Negative", "Positive"), values = c("#E76F51",'#CCDDBB')) +
  theme_minimal()

@@

# Save as final figure
ggarrange(mod1_longitudinal, mod2_longitudinal, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
ggsave(filename = "longitudinal_plot.tiff",
                          width=12, height=4, units='in', dpi=300)

### 2023-11-16 UpdatedModels/ABCDModelTraining.Rmd
Cleaned up original script, and added code for descriptive statistics. For revision script, updated code for variable importance, edited figures to save in tiff format and arrange in proper formatting for manuscript. In model training script, updated model names for clarity after incorporation of ComBat pipeline.

```{r}
load("/Volumes/devbrainlab/Lucy/BrainAGE/FYP/training_sample_baseline.Rds")

@@

set.seed(42)
df_split <- initial_split(
  training_sample_baseline, 
  prop = 0.80,
  # matching age distributions across train and test set
  strata = "interview_age"
)
df_train <- training(df_split)
df_validation <- testing(df_split)

@@

# select parsimonious params within one SE of best model
best_xgb_params_test <- xgb_tuned_results_test %>%
  select_by_one_std_err(metric = "mae", maximize = FALSE, tree_depth)

@@

Finalize workflow and fit final model
```{r}
final_xgb <- finalize_workflow(
  xgb_wf,
  best_xgb_params_test
)

final_xgb

fit_workflow <- fit(final_xgb, df_train_prep)

@@

final_xgb %>%
  fit(data = df_train) %>%
  extract_fit_parsnip() %>%
  vip(geom = "point")

@@

```{r}
final_res <- last_fit(final_xgb, df_split)

@@

Save models
```{r}
# three different save formats just in case
# 1. Rds
save(fit_workflow, file = "fit_workflow.rds")
# 2. rda
save(fit_workflow, file = "fit_workflow_2.rda")
# 3. raw xbg object, which can then be loaded with xgb.load
model_obj <- fit_workflow$fit$fit$fit
xgb.save(model_obj, "model_obj")
```

@@

brain_age_df_test <- as.data.frame(brain_age_df_test) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = analysis_sample_baseline$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

brain_age_df_workflow <- fit_workflow %>%
  predict(new_data = analysis_sample) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = analysis_sample$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Bias Correction
```{r}
#run model on validation set
abcd_brain_age_correction <-
  fit_workflow %>%
  predict(new_data = df_validation) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = df_validation$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

# create bias correct data frame
#Baseline
brain_age_corrected_df <- brain_age_df %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - abcd_bias_intercept) / abcd_bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

@@

>>>>

```{r}
#load("/Volumes/devbrainlab/Lucy/BrainAGE/FYP/training_sample_baseline.Rds")
load("/Volumes/devbrainlab/Lucy/BrainAGE/FYP/model2_features.Rds")

model2_features_noid <- model2_features %>% 
  select(-c(src_subject_id))

@@

set.seed(42)
df_split <- initial_split(
  model2_features_noid, 
  prop = 0.80,
  # matching age distributions across train and test set
  strata = "interview_age"
)
df_train <- training(df_split)
df_validation <- testing(df_split)

@@

# select parsimonious params within one SE of best model
best_xgb_params <- xgb_tuned_results_test %>%
  select_by_one_std_err(metric = "mae", maximize = FALSE, tree_depth)

@@

Finalize workflow and fit final model
```{r}
final_xgb_combat <- finalize_workflow(
  xgb_wf,
  best_xgb_params
)

final_xgb_combat

fit_workflow_combat <- fit(final_xgb_combat, df_train_prep)

@@

final_xgb_combat %>%
  fit(data = df_train) %>%
  extract_fit_parsnip() %>%
  vip(geom = "point")

@@

```{r}
final_res <- last_fit(final_xgb_combat, df_split)

@@

Save models
```{r}
# three different save formats just in case
# 1. Rds
save(fit_workflow_combat, file = "fit_workflow_combat.rds")
# 2. rda
save(fit_workflow_combat, file = "fit_workflow_2_combat.rda")
# 3. raw xbg object, which can then be loaded with xgb.load
abcd_model_obj_combat <- fit_workflow_combat$fit$fit$fit
xgb.save(abcd_model_obj_combat, "abcd_model_obj_combat")
```

@@

# combat version
brain_age_df_combat <-
  abcd_model_obj_combat %>%
  predict(newdata = as.matrix(model2_analysis %>% select(-c(src_subject_id, interview_age))))

brain_age_df_combat <- as.data.frame(brain_age_df_combat) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = model2_analysis$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

brain_age_df_workflow_combat <- fit_workflow_combat %>%
  predict(new_data = model2_analysis) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = model2_analysis$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Bias Correction
```{r}
#run model on validation set
abcd_brain_age_correction <-
  fit_workflow_combat %>%
  predict(new_data = df_validation) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = df_validation$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

@@

# create bias correct data frame
#Baseline
brain_age_corrected_df_combat <- brain_age_df_workflow_combat %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - abcd_bias_intercept) / abcd_bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

@@

Clean up & save
```{r}
# add IDs back
brain_age_corrected_df_combat$src_subject_id <- model2_analysis$src_subject_id

brain_age_corrected_df_combat <- brain_age_corrected_df_combat %>% 
  select(6, 1:5)

# save dataframe
save(brain_age_corrected_df_combat, file = "brain_age_corrected_df_combat.Rda")
